\documentclass[letterpaper]{article}

\usepackage{ulem}
\usepackage{contour}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.25in]{geometry}

\hypersetup{
  colorlinks = true,
  urlcolor   = RoyalBlue!75!white,
}

\raggedright
\raggedbottom
\urlstyle{same}
\setlength{\tabcolsep}{0in}
\AtBeginDocument{\normalem}

\newlength{\uppercaseHeight}
\AtBeginDocument{\settoheight{\uppercaseHeight}{A}}

% Ensure output is parsable
\pdfgentounicode=1
\input{glyphtounicode}

% Sections formatting
\titleformat{\section}{\vspace{-9pt}\scshape\raggedright\large}{}{0em}{}[\color{gray}\titlerule\vspace{-7pt}]

% Beautiful underline
\renewcommand{\ULdepth}{2pt}
\contourlength{1pt}

\newcommand{\beauline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\[-0.075em]
    \end{tabular*} \\[-0.05em]
}

\newcommand{\resumeHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*} \vspace{-3pt}
}

\newcommand{\resumeSmallHeading}[1]{
    \item {\small#1 \vspace{-0.75em}}
}

\newcommand\badgeStrut{\rule[-1pt]{0pt}{\uppercaseHeight}}
\newtcbox{\badge}{
  on line,
  enhanced,
  arc=3pt,
  top=2pt,
  left=5pt,
  right=5pt,
  bottom=2pt,
  boxsep=0pt,
  boxrule=0.25pt,
  colback=white!95!gray,
  enlarge bottom by=2pt,
  fontupper=\scriptsize\badgeStrut\color{black},
}
\newcommand{\badges}[1]{
  \foreach \b in #1 {
    \badge{\b}\hspace{-3pt}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.125in, label={}]}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-4pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\link}[2]{\href{#1}{\beauline{#2}}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

% ------------------------------------------------------------ %

\begin{center}
	\textbf{\Huge Malyutin Roman} \\[0.5em]
	\link{mailto:therealmal23@gmail.com}{therealmal23@gmail.com} ~
	\link{https://github.com/TheRealMal}{github.com/TheRealMal} ~
	\link{https://gitlab.com/TheRealMal}{gitlab.com/TheRealMal} ~
    \link{https://leetcode.com/TheRealMal}{leetcode.com/TheRealMal} ~
	\link{https://t.me/therealmal}{t.me/therealmal}
\end{center}

% ------------------------------------------------------------ %

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Bauman Moscow State Technical University}{Sep. 2020 - May 2026}
{Specialist of Computer Security}{Moscow, Russia}

\resumeSubheading
{School 21}{Aug. 2023 - Nowadays}
{Multidirectional programming institution}{Moscow, Russia}
\badges{{C, C++, Bash, Databases, Algorithms and Data Structures, Soft skills, DevOps}}

\resumeSubheading
{VK Education}{Oct. 2023 - Dec. 2023}
{Golang web services development}{Moscow, Russia}
\badges{{Go, Async, REST, Web Security, SQL, K8S, Docker, CI/CD, Microservices}}


\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Sonatype Nexus tools}{Aug. 2023}
{Internship at CryptoPro $|$ \link{https://github.com/TheRealMal/nexus-manager}{github.com/TheRealMal/nexus-manager}}{Moscow, Russia}
\badges{{Python, API, Nexus, Docker}}
\resumeItemListStart
\resumeItem{Tools for managing artifacts in Sonatype Nexus repositories}
\resumeItem{Designed and coded using Python language, versions packed to .whl files for Linux installation \& usage}
\resumeItem{Can be configured for any nexus server, supports filtration for platforms and targets}
\resumeItem{Supports multiple command line flags to specify script behavior}
\resumeItemListEnd

\resumeSubheading
{Telegram bot for reshipping service}{Jun. 2023}
{Commercial project}{Moscow, Russia}
\badges{{Python, Telethon}}
\resumeItemListStart
\resumeItem{User friendly telegram interface}
\resumeItem{Admin control panel to manage rates, orders, statuses etc.}
\resumeItem{Automatically parses banks/exchanges to update current rates}
\resumeItemListEnd

\resumeSubheading
{CLI Python bot}{Jan. 2022 -- Oct. 2022}
{PET project $|$ \link{https://github.com/TheRealMal/TheRealMalAIO}{github.com/TheRealMal/TheRealMalAIO}}{Moscow, Russia}
\badges{{Python, Discord.py, API, CLI UI}}
\resumeItemListStart
\resumeItem{Imitates human behavior and generates messages based on discord channel messages.}
\resumeItem{Automatically joins discord servers with some intermediate tasks: adding reaction to discord message, pushing buttons, sending necessary messages, solving captcha.}
\resumeItem{API for authorization and message generation.}
\resumeItem{Fully headless (All actions are made through requests w/o selenium etc.).}
\resumeItem{Selling 18 keys resulted in \textbf{200.000 rub.} profit.}
\resumeItemListEnd

\resumeSubheading
{Browser Extension}{Mar. 2022 -- May. 2022}
{PET project $|$ \link{https://github.com/TheRealMal/ExtensionTRM}{github.com/TheRealMal/ExtensionTRM}}{Moscow, Russia}
\badges{{JavaScript, HTML, CSS, API, Browser Extension}}
\resumeItemListStart
\resumeItem{Automates user actions when waiting and buying limited items. }
\resumeItem{Supports multiple sites and multiple profiles for user details.}
\resumeItem{Bypasses site bot \& fraud protection.}
\resumeItem{Selling 8 keys resulted in \textbf{105.000 rub.} profit.}
\resumeItemListEnd

\resumeSubheading
{Web Library System}{Dec. 2021}
{Coursework $|$ \link{https://github.com/TheRealMal/LibrarySystem}{github.com/TheRealMal/LibrarySystem}}{Moscow, Russia}
\badges{{JavaScript, HTML, CSS, API, Hash Algorithms}}
\resumeItemListStart
\resumeItem{Web application for searching and managing books.}
\resumeItem{Search was conducted using the Rabin-Karp algorithm and indexing.}
\resumeItemListEnd

\resumeSubheading
{Own services (Discord paid group)}{Jan. 2019 -- Jun. 2022}
{Commercial project}{Moscow, Russia}
\badges{{Python, REST, Web Scraping, Cuncurrency, JavaScript, ExpressJS, OAuth2, Web Vulnerabilities, WebSockets, }}
\resumeItemListStart
\resumeItem{Developed restock monitors (web scrappers) for different websites.}
\resumeItem{Did researches to find websites bot protection bypasses, queue bypasses, etc.}
\resumeItem{Developed web-dashboard and automatic payment system for group subscription.}
\resumeItem{Developed WebSockets API for CLI Bot (Authorization, users notification, secure some algorithms).}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Skills}
\resumeSubHeadingListStart

\resumeSmallHeading
{\textbf{Programming Languages}:\badges{{Python, Go, C, C++, JavaScript, Bash}}}

\resumeSmallHeading
{\textbf{Databases}:\badges{{PostgreSQL, SQLalchemy, pandas}}}

\resumeSmallHeading
{\textbf{Technologies}:\badges{{Docker, Kubernetes, ExpressJS, Sonatype Nexus, Burp Suite, Charles}}}

\resumeSmallHeading
{\textbf{Misc.}:\badges{{Linux, SQL, HTML/CSS, Grafana, REST API, WebSockets, JSON, HTTP, DNS, TCP/UDP}}}

\resumeSmallHeading
{\textbf{Spoken Languages}:\badges{{Russian (native speaker), English (upper-intermediate)}}}

\resumeSubHeadingListEnd

\section{Interests}
\resumeSubHeadingListStart

\resumeSmallHeading{\badges{{Backend Development, DevOps, Cryptography, Web-Security}}}

\resumeSubHeadingListEnd

\end{document}