\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{darkblue}{rgb}{0.0, 0.0, 0.5}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\LARGE Malyutin Roman}
\end{center}

\begin{flushleft}
    \textbf{Contact Information:}
\end{flushleft}

\begin{minipage}{.5\textwidth}
    123 Main Street \\
    City, State, ZIP Code \\
    Phone: (123) 456-7890 \\
    Email: johndoe@email.com
\end{minipage}

\begin{minipage}{.5\textwidth}
    \begin{flushright}
        \href{https://www.linkedin.com/in/johndoe}{\textcolor{darkblue}{LinkedIn}} \\
        \href{https://github.com/johndoe}{\textcolor{darkblue}{GitHub}}
    \end{flushright}
\end{minipage}

\begin{flushleft}
    \textbf{Summary:}
\end{flushleft}

Passionate and experienced software developer with a strong background in web and mobile application development. Proficient in multiple programming languages and frameworks. Excellent problem-solving and communication skills. Proven track record of delivering high-quality software solutions.

\begin{flushleft}
    \textbf{Education:}
\end{flushleft}

\begin{itemize}[label=--,left=0pt]
    \item \textbf{B.S. in Computer Science}, University Name, City, State, Year
\end{itemize}

\begin{flushleft}
    \textbf{Skills:}
\end{flushleft}

\begin{itemize}[label=--,left=0pt]
    \item Programming Languages: Java, Python, JavaScript
    \item Web Development: HTML, CSS, React, Node.js
    \item Mobile App Development: Android (Java/Kotlin)
    \item Database Management: SQL, MongoDB
    \item Version Control: Git
    \item Problem Solving
    \item Team Collaboration
\end{itemize}

\begin{flushleft}
    \textbf{Professional Experience:}
\end{flushleft}

\begin{itemize}
    \item \textbf{Software Developer}, Company Name, City, State \hfill Month Year - Present
    \begin{itemize}
        \item Developed and maintained web applications using React and Node.js, improving user experience and performance.
        \item Collaborated with cross-functional teams to design and implement new features.
        \item Utilized version control and code review best practices with Git.
    \end{itemize}

    \item \textbf{Mobile App Developer}, Company Name, City, State \hfill Month Year - Month Year
    \begin{itemize}
        \item Designed and developed Android applications using Java and Kotlin, achieving a 30% increase in user engagement.
        \item Worked closely with UX/UI designers to create intuitive and user-friendly interfaces.
        \item Conducted code reviews and provided mentorship to junior developers.
    \end{itemize}
\end{itemize}

\begin{flushleft}
    \textbf{Projects:}
\end{flushleft}

\begin{itemize}
    \item \textbf{E-commerce Website}, GitHub Repository \hfill Month Year - Present
    \begin{itemize}
        \item Created a responsive e-commerce website using React, allowing users to browse and purchase products online.
        \item Implemented secure authentication and payment processing.
    \end{itemize}

    \item \textbf{Task Management App}, GitHub Repository \hfill Month Year - Month Year
    \begin{itemize}
        \item Developed a task management app for Android using Java, enabling users to organize and track their tasks.
        \item Implemented real-time synchronization with a remote server.
    \end{itemize}
\end{itemize}

\begin{flushleft}
    \textbf{Languages:}
\end{flushleft}

\begin{itemize}
    \item English (Fluent)
\end{itemize}

\end{document}
